\section{Documents}

					\begin{center}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Problem & Description & Likelihood (1-9) & Impact (1-9) & Importance (Likelihood * Impact) & Preventive action & Remedial Action \\ \bottomrule
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \\
Communication Loss & Group members doesn't communicate with each other. Group don't establish good communication with the customer and supervisor & 3 & 7 & 21 & Actively establish communication and reach out to the parties. & Talk with the group about the communication, and try to get a good grip of what is failing. Establish communication media, so the group can talk with eachother.\\ 
\hline
Change requests & Change requests that does not meet the requirements of the product & 3 & 7 & 21 & Well defined requirements spesification, implementing it iterative. & Talk with the customer and ask what he thinks about the request changes.\\ 
\hline
Technical difficulties
 & Some problems may turn up to be very hard to solve. This can in turn lead to delays and frustration. And may sometimes be very time consuming. & 5 & 4 & 20 & Regulary have technical discussions with the group, that way the hard problems can be handled by the group as a whole.
 & If the problem is to hard, try to get help from other groups. Also evaluate if the problem can be handled differentely.\\ 
\hline
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Workstation are noisy & The workstation is filled with people who make alot of sound, so the developers team can't concentrate to the fullest. & 5 & 4 & 20 & Can preorder room, so we get our own workstation to work on. & Preorder room, and move the whole developers team there. If the noise is that bad.\\ 
\hline
Failing to do planned work & Members of the group fails to do schedueld work due to falling behind in subjects not related to the project or other things.  & 9 & 2 & 18 & Good scheduling habits. Sit down every week and see what's planned to do in the project the following week. Coordinate against what you have to do in other subject. & Make up for lost work during weekends or other available time slots\\ 
\hline
Insufficient product & Devolping a product that does not meet the requirements of the costumer & 2 & 9 & 18 & Good communication with the costumer, in sort of agile devolpment such as Scrum & \\ 
\hline
API change & The general API has to be changed, because it lack functionality. & 2 & 9 & 18 & Sufficient research about API before implementing it into the project. & Either drop the functionality that is missing, or start developing with the new API.\\ 
\hline
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Different app views & Customer and developers have different views of the apps purpose and funtions & 3 & 6 & 18 & Have regular meetings, inform and discuss all changes to project scope, goals and features. & Discuss with customer and find middle ground.\\ 
\hline
Scope & The amount of features requested are beyond what the development team can deliver in time & 6 & 3 & 18 & Be specific with the customer how much time we have, and explain deeply how much time it takes to develop a single feature & Discuss what are the nessasery features that must be in the product, and flush out what is the least nessasery.\\ 
\hline
Lack of competence & Don't have enough competence about the given software we are suppose to use during the project. & 8 & 2 & 16 & Meet every day, do workgroups together and learn by failing. & Talk with other members of the group, and hear if they have the competence. This will prevent hours of searching, when you can listen what the other members have to say. And direct you on the right path for the competence you need.\\ 
\hline
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Install of stedr & Not all group members can install the app on their own device. The purpose is to evaluate stedr. & 5 & 3 & 15 & Install it while you have a meeting, so all the group members can atleast watch the app on another device. & Go together 2 and 2, and watch the app on a phone whose able to install the app.\\ 
\hline
Missing deadlines & Some work may take longer time than expected, this this may cause delays later on in the project. & 3 & 5 & 15 & Have a steady and diciplined workflow and plan ahead. Overestimate work rather than underestimate. & All members meet and plan what is to be done, and do it at once. So we can deliver as soon as possible.\\ 
\hline
Customer turnover disruption & A key contact in SINTEF leaves the company, putting the project in a unclear state & 2 & 7 & 14 & Good communication. Multiple contacts with knowledge of the project & Quickly contact the customer and discuss how to proceed and how it's affected\\ 
\hline
Sickness & Group members or other crucial personell gets sick & 4 & 3 & 12 & Have regular updates about the progress of the work being done, and don't make important task rely completely on one person without a backup plan. Don't freeze and drink a lot of tea. & Talk to the person about the individual tasks, how much he can handle, and distribute the work the member can't.\\ 
\hline
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Group members falling out. & Members doesn't show for meetings, or goes of the grid without notice. & 2 & 6 & 12 & Good communication and agree on a schedule that suits everyone. & Take action at once, and make inquires to why the member didn't show.\\ 
\hline
Uneven workload & Uneven distribution of workload & 6 & 2 & 12 & Keep updated on the tasks given and work put in, and distribute work  & Make the member or members direct task. So it's easy for the member or members to do so. \\ 
\hline
Conflict over changes & Group members not in agreement over supposed changes in group management, work, responibility etc. & 3 & 4 & 12 & Have an open dialog. & Discuss in group and decide as a democracy.\\ 
\hline
Late for meeting & Members of the group are late for meetings with group/customer and supervisor & 6 & 2 & 12 & Good communication and agree on a schedule that suits everyone. & Take action at once, and make inquires to why the member came late.\\ 
\hline 
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Documents customer/supervisor meeting & You lack the sufficeint documents for the meeting with the customer. For presentation on how you want the app to be, mockups and reports about fieldwork etc. & 2 & 6 & 12 & Have the documents stored in the cloud so  you can acces it where ever you go. With your respective smartphone/tablet and pc's, & Discuss what you remember and try to make the best out of the meeting, as possible.\\ 
\hline
Equipment failure & Computers and other dependable devices malfunctions. & 4 & 2 & 12 & Keep documents and code in the cloud so you can work from another device if your primary device malfunction. & Get replacement as soon as possible.\\ 
\hline
Document sharing failed & Authorization of documents sharing is not complete, people don't have access to the groups documents. & 2 & 4 & 8 & Give all the authorization they need for the documents to be shared. So all can view, edit and share documents. & Find out where the problem lies, so everyone can get authorization for the given documents and folders.\\ 
\hline
						\end{tabulary}
						\begin{tabulary}{\textwidth}{L | R | C | C | C | L | R} \toprule
Lack of software  & nessasery for the develoment progress & 1 & 3 & 3 & Talk about what software is required for the development of the product. Ask the customer for this software.   & Ask the customer immediately for the required software, so the development progress don't have any major delays. \\ 
\hline

						\end{tabulary}
					\end{center}